Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-18 ms.tex
I added few changes to the analysis section describing the time series and photon errors.

Figure \ref{fig:specphot} also shows the dynamic spectra (relative source brightness as a function of wavelength and time.
{\sha} has a dynamic spectra resembling white noise with no significant variations in either the spectral or spatial direction at the $\lesssim1$\% level.
{\shb}, on the other hand, shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths. The periodic signal is nearly coincident with the 4.2~hr period measured by \citet{2015ApJ...799..154M}, enabling confirmation that the signal is astrophysical rather than systematic (see \citealt{2016ApJ...826..156S}).
Both sources exhibit some systematic features in the strong telluric absorption bands at 1.4 and 1.8~$\mu$m, likely caused by residual wavelength drifts from flexure and lower signals-to-noise.

@@

Individual narrow-band light curves for extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}.
The uncertainties in these curves are 0.2\% in high throughput regions of the spectrum and 0.6\% per exposure.
The lower values are areas of high throughput and flux whereas the low values are near telluric absorption features or the edges of the spectrum.
We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period of the brown dwarfs and compare it to the expected photon + read noise.
In these wavelength bins, the standard deviations of the points is about 2$\times$ the expected read noise and photon noise.
We attribute this to correlated errors between wavelengths. {\bf [WHAT? HOW DETERMINED?]}

>>>>

Figure \ref{fig:specphot} also shows the dynamic spectra (relative source brightness as a function of wavelength and time.
{\sha} has a dynamic spectra resembling white noise with no significant variations in either the spectral or spatial direction at the $\lesssim$0.5\% level.
{\shb}, on the other hand, shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths. The periodic signal is nearly coincident with the 4.2~hr period measured by \citet{2015ApJ...799..154M}, enabling confirmation that the signal is astrophysical rather than systematic (see \citealt{2016ApJ...826..156S}).
Both sources exhibit some systematic features in the strong telluric absorption bands at 1.4 and 1.8~$\mu$m, likely caused by residual wavelength drifts from flexure and lower signals-to-noise.

@@

Individual narrow-band light curves for extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}.
The uncertainties in these curves are 0.2\% in high throughput regions of the spectrum and 0.6\% per exposure.
The lower values are areas of high throughput and flux whereas the low values are near telluric absorption features or the edges of the spectrum.
We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period of the brown dwarfs and compare it to the expected photon + read noise.
In these wavelength bins, the standard deviations of the points is about 2$\times$ the expected read noise and photon noise.
We attribute this to correlated errors between wavelengths.
